Associations between Chlorophyll \emph{a} and various Microcystin-LR Health Advisory Concentrations

### 2015-09-16 manuscript/manuscript.Rmd
render with changes to fig width

We use this association to identify chlorophyll *a* concentrations that are associated with greater than even odds of exceeding a given health advisory level (Table \ref{tab:mc_chla_table}).  These represent `r round(100*(length(nla_dat$CHLA[nla_dat$CHLA>=mc_chla[1]])/length(nla_dat$CHLA)),1)`%, `r round(100*(length(nla_dat$CHLA[nla_dat$CHLA>=mc_chla[2]])/length(nla_dat$CHLA)),1)`%,
`r round(100*(length(nla_dat$CHLA[nla_dat$CHLA>=mc_chla[3]])/length(nla_dat$CHLA)),1)`%, and `r round(100*(length(nla_dat$CHLA[nla_dat$CHLA>=mc_chla[4]])/length(nla_dat$CHLA)),1)`% of sample lakes for the U.S EPA childrens drinking water, the WHO drinking water, the U.S. EPA Adult drinking water, and the WHO recreationsl standards, respecitvely.
<!-- (Figure \ref{fig:chla_micro_cdf}) -->

@@

```{r chla_micro_scatter, echo=FALSE, fig.width=8, fig.cap="Scatterplot showing association betweeen chlorophyll \\textit{a} and microcystin-LR. \\label{fig:chla_micro_scatter}"}
plot_scatter(nla_dat,xvar="log_chla",yvar = "log_micro",pt_col=viridis(1),
             x=expression(paste('Log10 Chl ', italic("a"),' (',mu,'g/L)')),
             y=expression(paste('Log10 microcystin-LR',' (',mu,'g/L)')))
```

@@

```{r epa_child_cp_plot, echo=FALSE, fig.width=8, fig.cap="Conditional probability plots showing association between the probability of exceeding various microcystin-LR (MLR) health advisory Levels. \\label{fig:multi_cp_plot}"}
multiplot(
  plot_cp(epa_child_cp,x = "Log 10 Chlorophyll", 
          y = "Probability of Exceeding 0.3 ug/L MLR",
          title="U.S. EPA Children's Drinking Water Advisory Level"),
  plot_cp(who_drink_cp, x = "Log 10 Chlorophyll", 
          y = "Probability of Exceeding 1 ug/L MLR", 
          title="WHO Drinking Water Advisory Level"),
  plot_cp(epa_adult_cp, x = "Log 10 Chlorophyll", 
          y = "Probability of Exceeding 1.6 ug/L MLR", 
          title="U.S. EPA Adult Drinking Water Advisory Level"),
  plot_cp(who_rec_low1_cp, x = "Log 10 Chlorophyll", 
          y = "Probability of Exceeding 2 ug/L MLR", 
          title="WHO Recreational Water Advisory Level"),
  cols=2
)
```

@@

```{r mc_chla_table, results='asis', echo=FALSE, tab.cap="Chlorophyll \textit{a} concentrations that are associated with a 50 percent probability of exceeding a microcystin-LR health advisory concentration. \\label{tab:mc_chla_table}"}
mc_chla_tbl <- data.frame(Source=mc_names,Type=mc_type,Microcystin=mc_guides,Chlorophyll=mc_chla)[1:4,]
#pandoc.table(mc_chla_tbl,justify = "left" ,split.table = 120, split.cells  = c(20,20,20))
knitr::kable(mc_chla_tbl)
```

>>>>

We use this association to identify chlorophyll *a* concentrations that are associated with greater than even odds of exceeding a given health advisory level (Table \ref{tab:mc_chla_table}).  These represent `r round(100*(length(nla_dat$CHLA[nla_dat$CHLA>=mc_chla[1]])/length(nla_dat$CHLA)),1)`%, `r round(100*(length(nla_dat$CHLA[nla_dat$CHLA>=mc_chla[2]])/length(nla_dat$CHLA)),1)`%,
`r round(100*(length(nla_dat$CHLA[nla_dat$CHLA>=mc_chla[3]])/length(nla_dat$CHLA)),1)`%, and `r round(100*(length(nla_dat$CHLA[nla_dat$CHLA>=mc_chla[4]])/length(nla_dat$CHLA)),1)`% of sample lakes for the U.S EPA childrens drinking water, the WHO drinking water, the U.S. EPA Adult drinking water, and the WHO recreational standards, respecitvely.
<!-- (Figure \ref{fig:chla_micro_cdf}) -->

@@

```{r chla_micro_scatter, echo=FALSE, fig.width=7, fig.cap="Scatterplot showing association betweeen chlorophyll \\textit{a} and microcystin-LR. \\label{fig:chla_micro_scatter}"}
plot_scatter(nla_dat,xvar="log_chla",yvar = "log_micro",pt_col=viridis(1),
             x=expression(paste('Log10 Chl ', italic("a"),' (',mu,'g/L)')),
             y=expression(paste('Log10 microcystin-LR',' (',mu,'g/L)')))
```

@@

```{r epa_child_cp_plot, echo=FALSE, fig.width=7, fig.cap="Conditional probability plots showing association between the probability of exceeding various microcystin-LR (MLR) health advisory Levels. \\label{fig:multi_cp_plot}"}
multiplot(
  plot_cp(epa_child_cp,x = "Log 10 Chlorophyll", 
          y = "Probability of Exceeding 0.3 ug/L MLR",
          title="U.S. EPA Children's Drinking Water Advisory Level"),
  plot_cp(who_drink_cp, x = "Log 10 Chlorophyll", 
          y = "Probability of Exceeding 1 ug/L MLR", 
          title="WHO Drinking Water Advisory Level"),
  plot_cp(epa_adult_cp, x = "Log 10 Chlorophyll", 
          y = "Probability of Exceeding 1.6 ug/L MLR", 
          title="U.S. EPA Adult Drinking Water Advisory Level"),
  plot_cp(who_rec_low1_cp, x = "Log 10 Chlorophyll", 
          y = "Probability of Exceeding 2 ug/L MLR", 
          title="WHO Recreational Water Advisory Level"),
  cols=1
)
```

@@

```{r mc_chla_table, results='asis', echo=FALSE, tab.cap="Chlorophyll \\textit{a} concentrations that are associated with a 50% probability of exceeding a microcystin-LR health advisory concentration. \\label{tab:mc_chla_table}"}
mc_chla_tbl <- data.frame(Source=mc_names,Type=mc_type,Microcystin=mc_guides,Chlorophyll=mc_chla)[1:4,]
#pandoc.table(mc_chla_tbl,justify = "left" ,split.table = 120, split.cells  = c(20,20,20))
knitr::kable(mc_chla_tbl)
```

### 2015-09-16 manuscript/manuscript.tex
render with changes to fig width

We use this association to identify chlorophyll \emph{a} concentrations
that are associated with greater than even odds of exceeding a given
health advisory level (Table \ref{tab:mc_chla_table}). These represent
27.8\%, 11.9\%, 8.3\%, and 7.4\% of sample lakes for the U.S EPA
childrens drinking water, the WHO drinking water, the U.S. EPA Adult
drinking water, and the WHO recreationsl standards, respecitvely.

@@

\begin{longtable}[c]{@{}llrr@{}}
\caption{Chlorophyll extit\{a\} concentrations that are associated with
a 50 percent probability of exceeding a microcystin-LR health advisory
concentration. \label{tab:mc_chla_table}}\tabularnewline
\toprule
Source & Type & Microcystin & Chlorophyll\tabularnewline
\midrule
\endfirsthead
\toprule
Source & Type & Microcystin & Chlorophyll\tabularnewline
\midrule
\endhead
U.S. EPA & Drinking & 0.3 & 23.68\tabularnewline
WHO & Drinking & 1.0 & 63.94\tabularnewline
U.S. EPA & Drinking & 1.6 & 89.71\tabularnewline
WHO & Recreational & 2.0 & 102.60\tabularnewline
\bottomrule
\end{longtable}

>>>>

We use this association to identify chlorophyll \emph{a} concentrations
that are associated with greater than even odds of exceeding a given
health advisory level (Table \ref{tab:mc_chla_table}). These represent
27.8\%, 11.9\%, 8.3\%, and 7.4\% of sample lakes for the U.S EPA
childrens drinking water, the WHO drinking water, the U.S. EPA Adult
drinking water, and the WHO recreational standards, respecitvely.

@@

\begin{longtable}[c]{@{}llrr@{}}
\caption{Chlorophyll \textit{a} concentrations that are associated with
a 50\% probability of exceeding a microcystin-LR health advisory
concentration. \label{tab:mc_chla_table}}\tabularnewline
\toprule
Source & Type & Microcystin & Chlorophyll\tabularnewline
\midrule
\endfirsthead
\toprule
Source & Type & Microcystin & Chlorophyll\tabularnewline
\midrule
\endhead
U.S. EPA & Drinking & 0.3 & 23.68\tabularnewline
WHO & Drinking & 1.0 & 63.94\tabularnewline
U.S. EPA & Drinking & 1.6 & 89.71\tabularnewline
WHO & Recreational & 2.0 & 102.60\tabularnewline
\bottomrule
\end{longtable}
